Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-09-01 ising/Fibonacci/about.tex

@@

\heading{Curve Diagrams}

@@

\begin{center}
\includegraphics[width=0.2\textwidth]{POP-3.eps}
\end{center}

@@

@@

This together with f-moves gives all the half-twists on
the curve $f$.

So we have a (linear) representation of the braid group:

@@

@@

where $f:L\to D$ is a continuous function 
whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components,
and the equivalence relation $\sim$ consists of 
isotopies that fix $\partial E.$ % Local (relative?) isotopies

This object has a simple combinatorial description 
as a string consisting of
the four labels {\bf (, ), H, T} such that 
the parentheses are balanced.
To construct the string, begin at a point on $\partial E$, and proceed
clockwise. Visiting a strand for the first time produces a {\bf ( } label,
and visiting a strand for the second time produces a {\bf ) } label.
The two labels {\bf H} and {\bf T} specify the
head and tail endpoints of $f$, each of which appears at most once in the string.

For example, the following planar diagram can be represented by
the string {\bf(())H}:

@@

@@

@@

@@

%We measure charge in regions bounded by curves, ie. elements of
%the first homology group $H_1(D_n).$

@@

%% ----------------------------------------------------------------------------
%
%\heading{Combinatorial Formulation}
%
%% ----------------------------------------------------------------------------
%
%\heading{Numerical Simulations}

>>>>

%\begin{abstract}
%
%\end{abstract}

@@

\heading{Abstract}

Technical contribution: 
(1) discretization of curve diagrams,
(2) classification theorem
(3) simulation

\heading{Introduction}

Fibonacci hard

Below bond-percolation threshold we expect to see clusters
of charges of size $O(log(n))$ with variance $O(log(log(n))$. CITATION

\heading{Curve diagrams}

@@

\begin{center}
\includegraphics[width=0.14\textwidth]{POP-3.eps}
\end{center}

@@

XXX F-moves can be nested

@@

This together with f-moves gives all the half-twists on
the curve $f$. Therefore, we may work solely with curve
diagrams, forgetting the underlying POP (tree) structure.

We have a (linear) representation of the braid group:

@@

XXX

@@

where $f:L\to D$ is a continuous function 
whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components,
and the equivalence relation $\sim$ consists of 
isotopies that fix $\partial E.$ % Local (relative?) isotopies
Each component of $f(L)\cap E$ we call a {\it strand.}

Elements of $P$ have a simple combinatorial description 
as a finite sequence (a word) consisting of
the four labels {\bf (, ), H, T} such that 
the parentheses are balanced.
To construct such a word, begin at a point on $\partial E$, and proceeding
clockwise: visiting a strand for the first time produces a {\bf ( } label,
and visiting a strand for the second time produces a {\bf ) } label.
The two labels {\bf H} and {\bf T} specify the
head and tail endpoints of $f$, each of which appears at most once in the word.

For example, the following planar diagram can be represented by
the word {\bf(())H}:

@@

Combinatorialy, we store an element of $C_n^{(l)}$ by patching
together words for planar diagrams in a compatible way: 
neighbouring tiles must agree on the strands that they share.

@@

Poisson process, pair creation $t_{\mathrm{sim}}$

Extraction of syndrome, PICTURE

Clustering of charges, CITE BravyiHaah

Multi-round

@@

Threshold appears at $t_{\mathrm{sim}}\simeq 0.125$

\heading{Conclusion}

\important{Acknowledgements}

@@

%In an abelian theory we measure charge in regions bounded by curves, ie. elements of
%the first homology group $H_1(D_n).$

@@
